Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-31 parts/sa.tex
update procs

The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
\begin{definition} \todo{À revoir avec la nouvelle sémantique}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}

@@

\newcommand{\V}{V}
\newcommand{\E}{E}
\newcommand{\cwV}{\V_\ctx^\w}
\newcommand{\cwE}{\E_\ctx^\w}
\newcommand{\VProc}{\V_\PHproc}
\newcommand{\VObj}{\V_\Obj}
%\newcommand{\VSol}{\V_{Sol}}
\newcommand{\VSol}{\V_{\Sol}}

\def\Bv{\sat{\cwV}}
\def\Be{\sat{\cwE}}
\def\BvProc{\textcolor{red}{\sat{\cwV}^\PHproc}}
\def\BvObj{\textcolor{red}{\sat{\cwV}^\Obj}}
%\def\BvSol{\sat{\cwV}^{Sol}}
\def\BvSol{\textcolor{red}{\sat{\cwV}^{\Sol}}}

\newcommand{\Bee}[2]{\Be^{#1}_{#2}}

\begin{definition}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:
  \begin{align}
    \w &\subset \cwV \label{eq:Vw} \\
%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \\
%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio}
  \end{align}
\end{definition}

>>>>

The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
\towrite{pré-définir la structure abstraite}
\begin{definition}
\label{def:allprocs}
  \begin{align*}
  \allprocs(\V, \E) = \{ p \in \PHproc &\mid p \in \V \vee \exists P \in \V \cap \Obj,\\
  &\qquad p = \PHtarget(P) \vee p = \PHbounce(P) \}
%    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
%    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  \end{align*}
\end{definition}

\begin{comment}
\begin{definition} \todo{À revoir avec la nouvelle sémantique}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}
\end{comment}

@@

\begin{definition}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:
  \begin{align}
    \w &\subset \cwV \label{eq:Vw} \\
%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \\
%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio}
  \end{align}
\end{definition}
